\documentclass{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\begin{document}

\title{Cryptographic Analysis}
\author{Colin Rice}
\author{Sam Milito}
\author{Jacob Shedd}

\maketitle


\section{Race Conditions}

The code as-is provides no protections on money, i.e., there are no mutex locks. For example, the withdrawl function:
bool processWithdraw (std::vector<std::string> info)
{
	float b = (float)atof(info.at(4).c_str());
	if(b > 1000.00) {
		return false;
	}

	std::vector<Account>::iterator it;
	for (it = Database.begin(); it != Database.end(); it++) {
		if(it->get_un() == info.at(1) && it->get_logged_in() && b <= it->get_balance() && it->get_withdraw() + b <= 1000.00) {
			it->reduce_balance(b);
			it->increase_withdraw (b);
			return true;
		}
	}
	return false;
}
That is, a user logged on multiple times could theoretically withdraw double the amount in their account, assuming that the timing went through correctly. The only protection against this is not allowing users to log in on multiple machines at a time. However, the login function is also succeptible to a race condition.
bool login (std::vector<std::string> info) 
{
	std::vector<Account>::iterator it;
	int pin = atoi(info.at(3).c_str());

	for (it = Database.begin(); it != Database.end(); it++) {
===>	if(it->get_un() == info.at(1) && it->get_pin() == pin && !it->get_logged_in() && !it->get_locked()) {
			it->set_logged_in_true ();
			return true;
		} 
		else if(it->get_un() == info.at(1) && it->get_pin() != pin && !it->get_logged_in()) {
			it->increase_login_attempts();
			if(it->get_login_attempts() >= 3) {
				it->lock();
			}
			return false;
		}
	}
	return false;
}
If the timing works out correctly, a user will pass all required checks (the highlighted line), and then set_logged_in_true will be called. During this time, any other ATMs can then theoretically pass the same checks. The end result is that a single user would be logged on at multiple ATMs. Due to how fast all of the operations are (the data sets are miniscule), a demonstration was not feasible. This issue is exacerbated by the thirty second timeout window for packets (i.e., the bank accepts a packet if it's no more than 30 seconds old), as the proxy could hold packets, making sure that they are sent to the bank at identical times.

With a user logged on to multiple ATMs, they can abuse the race conditions to withdraw or transfer double their account balance.

\section{Invalid Transfers}
A transfer to an invalid user succeeds initially, as the checks are done out of order, namely the highlighted lines:
bool processTransfer (std::vector<std::string> info)
{
	float b = (float)atof(info.at(4).c_str());
	if(b > 1000.00) {
		return false;
	}

	std::vector<Account>::iterator it;
	for (it = Database.begin(); it != Database.end(); it++) {
		if(it->get_un() == info.at(1) && it->get_logged_in() && b <= it->get_balance() && it->get_transfer() + b <= 1000.00) {
===>		it->reduce_balance(b);
===>		it->increase_transfer (b);
			std::vector<Account>::iterator foo;
			for (foo = Database.begin(); foo != Database.end(); foo++) {
				if(foo->get_un() == info.at(5) && foo->get_balance() + b <= MAX_BAL) {
					foo->increase_balance (b);
					return true;
				}
			}
		}
	}
	return false;
}
The active user has their account debited before the targetted user has their account credited. The result is that issuing a transfer to an invalid user will result in the active ATM user losing money, which then vanishes entirely from the system. In the image, Bob has \$40 vanish when he attempts to transfer it to Vriska, a nonexistant user.
[transferLoss.png]
{demonstration}

\section{Overly Generous Timeouts}
The timeout checking on both sides is overly generous. The ATM has a 30 second window
if(time(NULL) - messageTimeout < 30) // Bank Response needs to be in less that 30 seconds.
{
    // [...]
}
and the bank has no timeout handling at all. As such, packets can be held up to 30 seconds before being sent to the ATM, and indefinitely before being sent to the bank. This opens it up to much longer analysis than otherwise. While there is no specific exploit I have in mind, this is a much larger window than is needed for packets to be sent and received. In the proxy, a large amount of work can be done. Adding the following code in between receiving an ATM packet and forwarding the packet to the bank results in proper operation:
printf( "Sleeping for 29 seconds.\n" );
sleep( 29 );
[slowLogin.png]

\section{Account Enumeration Via Transfer}
$0 transfers can be used to verify whether or not a given user has an account at the bank. For example, Alice tries to send $0 to Eve (which succeeds) and Vriska (which fails), showing that Eve has an account, but Vriska does not. In the image, Alice verifies that Bob is a valid user (as the transfer succeeds) and that Vriska is not a valid user, as the transfer fails.
[transferUser.png]
{demonstration}

\section{Dysfunctional Card Verification}
The actual contents of a card file are ignored. The only verification done on the card is if it has anything in it. That is, any card put into the machine will satisfy it, as long as it doesn't have a blank "magnetic strip" (i.e., contents). This is a massive security flaw, as it is a failure of two-factor security. The only protection that ATMs have are PINs, which only have 10^6 options.
{demonstration}

\section{Poor Scaling}
While not an issue with the current scale of the project, all account information is stored in a vector. With O(n) lookups, this will become incredibly slow with very large amounts of users.

\section{Crashing the Bank}
Adding a single line of code to the proxy will crash the bank. The bank cannot handle a malformed handshake message. The follow section of code in the proxy:
while(1)
{
	//read the packet from the ATM
    // [...]
	
	// Crashes bank
    strcpy( packet, "" );
    
	//forward packet to bank
    // [...]
	
	//get response packet from bank
    // [...]
	
	// Crashes ATM
	strcpy( packet, "" );
	
	//forward packet to ATM
    // [...]
}
can be easily manipulated to crash the bank (or, similarly, the ATMs, as detailed slightly later). Adding the line of code before forwarding the packet to the bank crashes the bank as soon as an ATM user attempts to log in. 
[crashBank.png]
Similarly, ATMs can be crashed by adding the line of code before forwarding the packet to the ATM.
[crashATM.png]
If both lines are left in, the bank crashes with a core dump, and the ATM crashes with no error message. This issue is due to not checking the validity of initial handshake messages. When it receives a blank message, it still tries to proceed with setting up a secure connection. The cryptographic functions crash, and the ATM and/or bank crash with them.
{demonstration}

\section{RNG Flaws}

Their random number generator when asked for 32 bytes of data, outputs 32
random hex bytes. This means that each byte only has 16 possibilities instead
of 256.
Thus everything they generate using these functions, AES Keys, nonces, etc..
Only has 128 bits of randomness instead of 256 bits if they are reading back 256 bits.

\section{Handshake Hijacking}

When the bank and atm establish a handshake the atm sends the bank a 
nonce encrypted with the banks rsa key. Then the bank send back an
encryption key and the nonce, as well as its own generated nonce

Note that there is no explicit authentication.

Assuming you have the atm's public key it is possible to pretend to be a bank. You can simply send back a key encrypted with the atm's public key and the nonce.

Since there is no rsa authentication, or any other form of authentication,
if you can guess the nonce you can pretend to be a bank. Normally this would
take 2**256 attempts, but due to the aforementioned flaw in the RNG it only
take 2**128 attempts. Even worse if you are starting an atm on an embedded
system up on restart, the entropy will be low and it is possible to guess
the output of the systems random number generator. Thus you can pretend
to be the bank.

This is super usefull due to the plethora of exploits available. You can 
make the atm give out infinite money, you can read everyone's card numbers 
and pins since they are sent over the network unhashed.



\end{document}
